Analysis paper

### 2021-06-25 analysis/analysis.Rmd
update plots

  plot_helper <- function(tmp = scores, xvar = x, y, rel = relative) {
    if (rel) {
      tmp <- tmp %>%
        arrange(target_type, get(x)) %>%
        group_by(target_type, get(x)) %>%
        mutate_at(y, ~ . - .[model == "Hub-ensemble"])
    }

    tmp %>%
      ggplot(aes_string(x = xvar, y = y, group = "model", color = "model")) +
      geom_point() +
      geom_line() +
      facet_wrap(facet_formula, scales = "free_y") +
      theme_minimal() +
      theme(legend.position = "bottom") +
      scale_color_manual(values = coldeaths)
  }

@@

>>>>

  setnames(scores, old = "model", new = "Model")

  plot_helper <- function(tmp = scores, xvar = x, y, rel = relative) {
    if (rel) {
      tmp <- tmp %>%
        arrange(target_type, get(x)) %>%
        group_by(target_type, get(x)) %>%
        mutate_at(y, ~ . - .[Model == "Hub-ensemble"])
    }

    tmp %>%
      ggplot(aes_string(x = xvar, y = y, group = "Model", color = "Model")) +
      geom_point() +
      geom_line() +
      facet_wrap(facet_formula, scales = "free_y") +
      theme_minimal() +
      theme(legend.position = "bottom") +
      scale_color_manual(values = coldeaths)
  }

@@

  setnames(scores, old = "model", new = "Model")
